---
title: "Module 0, Part 3: Practice with Real Data"
linktitle: "M0.3: Data Wrangling in R"
menu:
  content:
    parent: Module 0
    weight: 4
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In part 3, we'll introduce and practice many of the basic data management tools you'll need throughout the class. We'll do this while we work through the first homework assignment.

## Objectives
- Get (more) comfortable with `R`, `RStudio`, `Git`, and `GitHub`
- Work with some Medicare Advantage data

## Activities 
- Data manipulation with the `tidyverse`
- Create your own [Medicare Advantage repository](https://github.com/imccart-class/ma) and begin working with data. Some specific steps...
    1. Create an SSH key on your computer and pair with GitHub
    2. Create GitHub repository
    3. Clone to your local computer
    4. Create folder structure (check [Assignments Page](/assignment/) for more detail)
    5. Download data from OneDrive (check link on Canvas) and move to `data/input` folder
    6. Download code from the GitHub repository for the assignment and move to `data-code` folder


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/00-introduction/00-3-ma-data.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction/00-3-ma-data.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction/00-3-ma-data.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

