---
title: "Module 0, Part 1: Preparing for the Semester"
linktitle: "M0.1: Software Setup"
menu:
  content:
    parent: Module 0
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In part 1, we'll get everyone set up with `R`, `RStudio`, and `Git`.

## Objectives
- Introduce the class, goals, structure, etc.
- Review data manipulation in `R` using the `tidyverse`
- Demonstrate `RStudio` and clone repo


## Activities 
- Set up `R`, `RStudio`, and `Git` on your own machines
- Clone first repository


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/00-introduction/00-1-setup.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction/00-1-setup.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/00-introduction/00-1-setup.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

