---
title: "Module 1, Part 2: Introduction to Causal Inference"
linktitle: "M1.2: Causal Inference"
menu:
  content:
    parent: Module 1
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In part 2, we'll lay the foundation for all of the methods in this class...the potential outcomes framework. We'll discuss what this means and what we'll seek to estimate going forward.


## Objectives
- Explain potential outcomes
- Derive and explain the average treatment effect 
- Explain the differences between an average treatment effect and the average treatment effect on the treated


## Activities 
- Continue working with the [Hospital Cost Report Information System (HCRIS)](https://github.com/imccart-test/hcris) repository.


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing2.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing2.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/01-hospital-pricing/01-hospital-pricing2.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>
