---
title: "Module 2, Part 3: Estimating Demand for Cigarettes with IV"
linktitle: "M2.3: Application"
menu:
  content:
    parent: Module 2
    weight: 3
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In part 3, we employ the IV estimator in the context of demand estimation for cigarettes. We also introduce the idea of a "fixed effect" in a regression specification.


## Objectives
- Understand and use an IV estimator in R
- List and explain the key assumptions for a "good" instrument
- Define and explain a fixed effect in a regression context


## Activities 
- Continue work with the [CDC Tax Burden on Tobacco](https://github.com/imccart/CDC-Tobacco) data
- Estimate the price elasticity of demand for cigarettes using taxes as an instrument for price


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::


<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/02-smoking/02-smoking3.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/02-smoking/02-smoking3.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/02-smoking/02-smoking3.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

