---
title: "Module 2, Part 2: Instrumental Variables"
linktitle: "M2.2: IV"
menu:
  content:
    parent: Module 2
    weight: 2
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In part 2, we formally introduce instrumental variables and discuss some of the thorny issues associated with IV in practice (namely, testing for instrument validity and interpreting the results).


## Objectives
- Understand and describe the problem of weak instruments and how to test for weak instruments empirically
- Define and explain a local average treatment effect


## Activities 
- Continue work with the [CDC Tax Burden on Tobacco](https://github.com/imccart/CDC-Tobacco) data
- Data simulation and practical issues with IV


## Slides
Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::


<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/02-smoking/02-smoking2.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/02-smoking/02-smoking2.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/02-smoking/02-smoking2.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

