---
title: "Module 3, Part 3: RD in Practice"
linktitle: "M3.3: Star Ratings"
menu:
  content:
    parent: Module 3
    weight: 4
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

In Part 3 of this module, we'll work with a real-life example of RD using Medicare Advantage star ratings.

## Objectives
- Explain optimal bin width and bandwidth calculations
- Define "manipulation" of the running variable
- Define what we mean by "covariate balance" and why it matters for RDD


## Activities 
- Implement an RD strategy with Medicare Advantage star ratings
- Test for manipulation of the running variable
- Test for covariate balance


## Slides

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::


<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/03-ma-quality/03-ma-quality3.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/03-ma-quality/03-ma-quality3.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/03-ma-quality/03-ma-quality3.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

