---
title: "Module 4, Part 3: Difference-in-Differences in Practice"
linktitle: "M4.3: DD IRL"
menu:
  content:
    parent: Module 4
    weight: 3
type: docs
bibliography: "../../static/bib/BibTeX_Library.bib"
csl: "../../static/bib/chicago-syllabus-no-bib.csl"
output:
  blogdown::html_page:
    toc: false
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

The goal of Part 3 of this module is to use a DD strategy with real-life data and discuss some current issues with the implementation of DD designs in practice


## Objectives
- Explain a fixed effect and an event study in the context of panel data regressions
- Understand some of the difficulties when interpreting the results of regression-based DD estimates

## Activities 
- Implement DD using real-life data on Medicaid expansion
- Estimate an event study with constant treatment timing
- Estimate an event study with differential treatment timing

## Slides

Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the embedded slides and navigate through them with your left and right arrow keys.

:::fyi
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::


<center>

```{r}
knitr::include_url("https://imccart.github.io/econ470-content/04-medicaid-uninsurance/04-medicaid-uninsurance3.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/04-medicaid-uninsurance/04-medicaid-uninsurance3.html"><i class="fas fa-external-link-alt"></i> View all slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/econ470-content/04-medicaid-uninsurance/04-medicaid-uninsurance3.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of all slides</a></p>

</center>

